FTLR proof cases

### 2018-05-17 fully-abstract-comp/ftlr-proof-cases.tex
Added more cases to FTLR proof

Let $n' \leq n$ be given and assume
\begin{enumerate}
\item $\npair[n']{\stpair{\reg}{\reg}} \in \lrrg{\trust}(W_R)$ \label{item:reg-ass}
\item $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$\label{item:mem-ass}
\item $W \oplus W_R \oplus W_M$ is well-defined\label{item:worlds-def}
\end{enumerate}
Further let
\begin{itemize}
\item $\Phi_S = (\ms_S,\reg_S\updReg{\pcreg}{c},\stk,\ms_\stk)$
\item $\Phi_T = (\ms_T,\reg_T\updReg{\pcreg}{c})$
\end{itemize}
and pick
\begin{itemize}
\item $\Phi_S' = \xjumpResult{c}{c}{\Phi_S}$
\item $\Phi_T' = \xjumpResult{c}{c}{\Phi_T}$
\end{itemize}
and show
\[
  \npair[n']{(\Phi_S',\Phi_T')} \in \lro
\]
In order to do this, we first, we prove that one of the following holds:
\begin{itemize}
\item $\Phi_S \step \failed$ and $\Phi_T \step\failed$
\item $\Phi_S \step \halted$ and $\Phi_T \step\halted$
\item All of the following hold:
  \begin{itemize}
  \item $\callCond{\Phi_S,r_1,r_2,\aaddr}$
  \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
  \item $\exec{\Phi_S(\pcreg)}$
  \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
  \item TODO: other useful info
  \end{itemize}
\item All of the following hold: (includes simple cases: gettype, geta, getb, gete, getp, getl, lt, plus, minus, that can be handled uniformly)
  \begin{itemize}
  \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
  \item $z \in \ints$
  \end{itemize}
\item All of the following hold: (includes cap-manipulation cases: move, cca, restrict, seta2b, cseal, split, splice, that can be handled mostly uniformly)
  \begin{itemize}
  \item \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r_1\cdots r_k}{w_1\cdots w_k}}\neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r_1\cdots r_k}{w_1'\cdots w_k'}} \neq \failed$
  \item One of the following holds:
    \begin{itemize}
    \item (restrict,cca,seta2b) $w_1 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
    \item (restrict,cca,seta2b) $w_1 = \stkptr{\perm,\baddr,\eaddr,\aaddr}$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
    \item ...
      \end{itemize}
  \end{itemize}
\item Other cases: store, load, jmp, jnz, xjmp
\end{itemize}

>>>>

Let $n' \leq n$ be given and assume
\begin{enumerate}
\item $\npair[n']{\stpair{\reg}{\reg}} \in \lrrg{\trust}(W_R)$ \label{item:reg-ass}
\item $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$\label{item:mem-ass}
\item $W \oplus W_R \oplus W_M$ is well-defined\label{item:worlds-def}
\end{enumerate}
Further let
\item $\Phi_S = (\ms_S,\reg_S\updReg{\pcreg}{c},\stk,\ms_\stk)$
\item $\Phi_T = (\ms_T,\reg_T\updReg{\pcreg}{c})$
and pick
\item $\Phi_S' = \xjumpResult{c}{c}{\Phi_S}$
\item $\Phi_T' = \xjumpResult{c}{c}{\Phi_T}$
and show
  \npair[n']{(\Phi_S',\Phi_T')} \in \lro
In order to do this, we first, we prove that one of the following holds:
\item $\Phi_S \step \failed$ and $\Phi_T \step\failed$
\item $\Phi_S \step \halted$ and $\Phi_T \step\halted$
\item All of the following hold:
  \item $\callCond{\Phi_S,r_1,r_2,\aaddr}$
  \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
  \item $\exec{\Phi_S(\pcreg)}$
  \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
  \item TODO: other useful info
\item All of the following hold: (includes simple cases: gettype, geta, getb, gete, getp, getl, lt, plus, minus, that can be handled uniformly)
  \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
  \item $z \in \ints$
\item All of the following hold: (includes cap-manipulation cases: move, cca, restrict, seta2b, cseal, split, splice, that can be handled mostly uniformly)
  \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r_1\cdots r_k}{w_1\cdots w_k}}\neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r_1\cdots r_k}{w_1'\cdots w_k'}} \neq \failed$
  \item One of the following holds:
    \item (restrict,cca,seta2b) $w_1 = ((\perm',\lin),\baddr,\eaddr,\aaddr')$, $w_1' = ((\perm',\lin),\baddr,\eaddr,\aaddr')$, $\Phi_S(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\Phi_T(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\perm' \sqsubseteq\perm$, $k = 1$
    \item (restrict,cca,seta2b) $w_1 = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$, $w_1' = ((\perm',\linear),\baddr,\eaddr,\aaddr')$, $\Phi_S(r_1) = \stkptr{\perm,\baddr,\eaddr,\aaddr}$ and $\Phi_T(r_1) = ((\perm,\linear),\baddr,\eaddr,\aaddr)$ and $\perm' \sqsubseteq\perm$, $k = 1$
    \item (move) $w_1 = \Phi_S(r_1)$, $w_1' = \Phi_S(r_1)$, and
      $\isLinear{w_1} \Rightarrow w_2 = w_2' = 0$, and $\neg
      \isLinear{w_1} \Rightarrow (w_2 = \Phi_S(r_2) \wedge w_2' = \Phi_T(r_2)$)
      and $k = 2$.
    \item (cseal) $w_1 = \sealed{\sigma,\Phi_S(r_1)}$, $w_1' = \sealed{\sigma,\Phi_T(r_1)}$, $\Phi_S(r_2) = \Phi_T(r_2) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $k=1$
    \item (split) $\Phi_T(r_3) = \Phi_S(r_3) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\baddr \leq n$, $n < \eaddr$, $w_1 = w_1' = ((\perm,\lin),\baddr,n,\aaddr)$, $w_2 = w_2' = ((\perm,\lin),n+1,\eaddr,\aaddr)$, $k=2$.
    \item (split) $\Phi_T(r_3) = \Phi_S(r_3) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $\sigma_\baddr \leq n$, $n < \sigma_\eaddr$, $w_1 = w_1' = \seal{\sigma_\baddr,n,\sigma}$, $w_2 = w_2' = \seal{n+1,\sigma_\eaddr,\sigma}$, $k=2$.
    \item (split) $\Phi_S(r_3) = \stkptr{\perm,\baddr,\eaddr,\aaddr}$, $\Phi_T(r_3) = ((\perm,\linear),\baddr,\eaddr,\aaddr)$, $\baddr \leq n$, $n < \eaddr$, $w_1 = \stkptr{\perm,\baddr,n,\aaddr}$, $w_1' = ((\perm,\linear),\baddr,n,\aaddr)$, $w_2 = \stkptr{\perm,n+1,\eaddr,\aaddr}$, $w_2' = ((\perm,\linear),n+1,\eaddr,\aaddr)$, $k=2$.
    \item (splice) $\Phi_T(r_2) = ((\perm,\linear),\baddr_2,\eaddr_2,\_)$,
      $\Phi_S(r_2) = \stkptr{\perm,\baddr_2,\eaddr_2,\_}$, and
      $\Phi_T(r_3) = ((\perm,\linear),\eaddr_2+1,\eaddr_3,\aaddr_3)$,
      $\Phi_S(r_3) = \stkptr{\perm,\eaddr_2+1,\eaddr_3,\aaddr_3}$, and
      $\baddr_2 \leq \eaddr_2$, and
      $\eaddr_2+1 \leq \eaddr_3$, and
      $w_1=((\perm,\linear),\baddr_2,\eaddr_3,\aaddr_3)$, $w_1'=
      \stkptr{\perm,\baddr_2,\eaddr_3,\aaddr_3}$, and
      $w_2 = w_2' = w_3 = w_3' = 0$, and
      $k=3$
    \item (splice) $\Phi_T(r_2) = \Phi_S(r_2) =
      ((\perm,\lin),\baddr_2,\eaddr_2,\_)$, and
      $\Phi_T(r_3) = \Phi_S(r_3) = ((\perm,\lin),\eaddr_2+1,\eaddr_3,\aaddr_3)$,
      $\baddr_2 \leq \eaddr_2$, and $\eaddr_2+1 \leq \eaddr_3$, and
      $w_1=w_1'=((\perm,\lin),\baddr_2,\eaddr_3,\aaddr_3)$, and
      $\lin = \linear \Rightarrow w_2 = w_2' = w_3 = w_3' = 0$, and
      $\lin = \normal \Rightarrow (w_2 = w_2' = \Phi_T(r_2) \text{ and } w_3 =
      w_3' = \Phi_T(r_3))$, and $k=3$
    \item (splice) $\Phi_T(r_2) = \Phi_S(r_2) = \seal{\sigma_{\baddr,2},\sigma_{\eaddr,2},\_}$, and $\Phi_T(r_3) = \Phi_S(r_3) = \seal{\sigma_{\eaddr,2}+1,\sigma_{\eaddr,3},\sigma_{\aaddr,3}}$, and $\sigma_{\baddr,2} \leq \sigma_{\eaddr,2}$, and $\sigma_{\eaddr,2} + 1 \leq \sigma_{\eaddr,3}$and $w_1 = w_1' = \seal{\sigma_{\baddr,2}, \sigma_{\eaddr,3}, \sigma}$
\item All of the following hold: (includes memory-manipulation cases: store, load, that can be handled mostly uniformly)
  \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' =
    \updPcAddr{\Phi_S\updReg{r_1,r_2}{w_1,w_2}\update{\mem.\aaddr}{w}}$
  \item $\Phi_T' =
    \updPcAddr{\Phi_T\updReg{r_1',r_2'}{w_1',w_2'}\update{\mem.\aaddr}{w'}}$
  \item One of the following hold:
    \item (store) $w_1 = w_1' = \Phi_S(r_1) = \Phi_T(r_1) =
      ((\perm,\lin),\baddr,\eaddr,\aaddr)$, and $\perm \in \writeAllowed{}$,
      $\withinBounds{w_1}$, and\\
      $w = \Phi_S(r_2)$, and $w' = \Phi_T(r_2)$, and $\isLinear{w} \Rightarrow
      w_2 = w_2' = 0$, and $\neg \isLinear{w} \Rightarrow (w_2 = \Phi_S(r_2)
      \text{ and } w_2' = \Phi_T(r_2))$.
    \item (load) $w_2 = w_2' = \Phi_T(r_2) = \Phi_S(r_2) =
      ((\perm,\lin),\baddr,\eaddr,\aaddr)$, and $\perm \in \readAllowed{}$,
      $\withinBounds{((\perm,\lin),\baddr,\eaddr,\aaddr)}$, and \\
      $w_1 = \Phi_S.\mem(\aaddr)$, and $w_1' = \Phi_T.\mem(\aaddr)$, and \\
      $\isLinear{w_1} \Rightarrow w = w' = 0$, and \\
      $\neg \isLinear{w_1} \Rightarrow w = w_1 \text{ and } w' = w_1'$
\item All of the following hold: (includes memory-manipulation cases: store, load, that can be handled mostly uniformly (stack))
  \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' =
    \updPcAddr{\Phi_S\updReg{r_1,r_2}{w_1,w_2}\update{\ms_\stk.\aaddr}{w}}$
  \item $\Phi_T' =
    \updPcAddr{\Phi_T\updReg{r_1',r_2'}{w_1',w_2'}\update{\ms_\stk.\aaddr}{w'}}$
  \item One of the following hold:
    \item (store) $w_1 = \Phi_T(r_1) = ((\perm,\linear),\baddr,\eaddr,\aaddr)$, $w_1' =  \Phi_S(r_1) = \stkptr{\perm,\baddr,\eaddr,\aaddr}$, and $\perm \in \writeAllowed{}$,
      $\withinBounds{w_1}$, and\\
      $w = \Phi_S(r_2)$, and $w' = \Phi_T(r_2)$, and $\isLinear{w} \Rightarrow
      w_2 = w_2' = 0$, and $\neg \isLinear{w} \Rightarrow (w_2 = \Phi_S(r_2)
      \text{ and } w_2' = \Phi_T(r_2))$.
    \item (load) $ w_2' = \Phi_T(r_2) =
      ((\perm,\linear),\baddr,\eaddr,\aaddr)$, and $w_2 = \Phi_S(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr}$, and $\perm \in \readAllowed{}$,
      $\withinBounds{((\perm,\lin),\baddr,\eaddr,\aaddr)}$, and $\aaddr \in
      \dom(\Phi.\ms_\stk)$, and $\aaddr \in \dom(\Phi.\ms_\stk)$, and\\
      $w_1 = \Phi_S.\ms_\stk(\aaddr)$, and $w_1' = \Phi_T.\ms_\stk(\aaddr)$, and \\
      $\isLinear{w_1} \Rightarrow w = w' = 0$, and \\
      $\neg \isLinear{w_1} \Rightarrow w = w_1 \text{ and } w' = w_1'$

\item All of the following hold: (includes memory-manipulation cases: jmp, jnz, xjmp, that can be handled mostly uniformly)
  \begin{itemize}
  \item 
  \end{itemize}
\end{itemize}
